Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
Pack together screenshots of Meadow

\begin{figure}
\centering{}\includegraphics[scale=0.5]{pix/detail2}\caption{\label{fig:detail-of-interface}Detail of the interface for 
contract
execution simulation.}
\end{figure}

Additionally, to facilitate the introduction of inputs, Meadow provides
two different interfaces:
\begin{itemize}
\item The manual interface (see Figure~\ref{fig:detail-of-manual-interface}),
provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (see Figure~\ref{fig:detail-of-smart-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{pix/detail3}
\par\end{centering}
\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.5]{pix/detail4}\caption{\label{fig:detail-of-smart-interface}Detail of the smart 
interface.}
\end{figure}

>>>>

\begin{figure}
\centering{}\includegraphics[scale=0.52]{pix/detail}\caption{\label{fig:detail-of-interface}Detail of the interface for 
contract
execution simulation.}
\end{figure}

Additionally, to facilitate the introduction of inputs, Meadow provides
two different interfaces:
\begin{itemize}
\item The manual interface, provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (shown in Figure~\ref{fig:detail-of-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
%\begin{figure}
%\begin{centering}
%\includegraphics[scale=0.5]{pix/detail3}
%\par\end{centering}
%\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
%\end{figure}

%\begin{figure}
%\centering{}\includegraphics[scale=0.5]{pix/detail4}\caption{\label{fig:detail-of-smart-interface}Detail of the smart 
%interface.}
%\end{figure}
